Preliminary results for predicting adverse CDI outcomes

### 2022-04-26 workflow/notebooks/preliminary_2022-04.Rmd
Use calculated idsa severity

```{r data}
otu_dat <- read_csv(here('data', 'SraRunTable.csv')) %>% 
              rename(sample_id = sample_title) %>% 
  left_join(fread(here('data', 'mothur', 'cdi.opti_mcc.shared')) %>% 
  rename(Run = Group), by = 'Run')
attrib_dat <- read_csv(here('data', 'raw', 'mishare', 
                            'clinical_outcomes.csv')) %>% 
  select(-CDIFF_SAMPLE_DATE, -CDIFF_COLLECT_DTM)
unattrib_dat <- read_csv(here('data', 'raw', 'mishare', 
                              'clinical_outcomes_pt2.csv'))  %>% 
  select(-CDIFF_SAMPLE_DATE, -CDIFF_COLLECT_DTM)
metadat <- bind_rows(attrib_dat, unattrib_dat) %>% 
  select(SAMPLE_ID, SUBJECT_ID, 
         IDSA_severe, ATTRIB_SEVERECDI, UNATTRIB_SEVERECDI) %>% 
  rename(sample_id = SAMPLE_ID, 
         subject_id = SUBJECT_ID,
         idsa = IDSA_severe,
         attrib = ATTRIB_SEVERECDI,
         unattrib = UNATTRIB_SEVERECDI) %>% 
  full_join(read_tsv(here('data', 'process', 'final_CDI_16S_metadata.tsv')) %>% 
              rename(sample_id = `CDIS_Sample ID`, 
                     subject_id = `CDIS_Study ID`,
                     collection_date = `CDIS_collect date`), 
            by = c('sample_id', 'subject_id')) %>% 
  select(sample_id, subject_id, collection_date, cdiff_case, group, idsa, attrib, unattrib) %>% 
  filter(!is.na(cdiff_case)) %>% 
  mutate(allcause = case_when((attrib == 1 | unattrib == 1) ~ 'yes',
                              (attrib == 0 & unattrib == 0) ~ 'no',
                              TRUE ~ NA_character_)
         )
```

```{r first_samples}
multi_samples <-
  metadat %>% 
  group_by(subject_id) %>% 
  filter(group == "case") %>% 
  tally() %>% 
  filter(n > 1)

>>>>

```{r data}
otu_dat <- read_csv(here('data', 'SraRunTable.csv')) %>% 
              rename(sample_id = sample_title) %>% 
  left_join(fread(here('data', 'mothur', 'cdi.opti_mcc.shared')) %>% 
  rename(Run = Group), by = 'Run')
attrib_dat <- read_csv(here('data', 'raw', 'mishare', 
                            'clinical_outcomes.csv')) %>% 
  select(-CDIFF_SAMPLE_DATE, -CDIFF_COLLECT_DTM)
unattrib_dat <- read_csv(here('data', 'raw', 'mishare', 
                              'clinical_outcomes_pt2.csv'))  %>% 
  select(-CDIFF_SAMPLE_DATE, -CDIFF_COLLECT_DTM)
metadat <- bind_rows(attrib_dat, unattrib_dat) %>% 
  select(SAMPLE_ID, SUBJECT_ID, ATTRIB_SEVERECDI, UNATTRIB_SEVERECDI) %>% 
  rename(sample_id = SAMPLE_ID, 
         subject_id = SUBJECT_ID,
         attrib = ATTRIB_SEVERECDI,
         unattrib = UNATTRIB_SEVERECDI) %>% 
  full_join(read_tsv(here('data', 'process', 'final_CDI_16S_metadata.tsv')) %>% 
              rename(sample_id = `CDIS_Sample ID`, 
                     subject_id = `CDIS_Study ID`,
                     collection_date = `CDIS_collect date`), 
            by = c('sample_id', 'subject_id')) %>% 
  full_join(read_csv(here('data', 'process', 'case_idsa_severity.csv')) %>% 
              rename(sample_id = sample,
                     idsa = idsa_severity),
            by = 'sample_id') %>% 
  select(sample_id, subject_id, collection_date, cdiff_case, idsa, attrib, unattrib) %>% 
  filter(!is.na(cdiff_case)) %>% 
  mutate(allcause = case_when((attrib == 1 | unattrib == 1) ~ 'yes',
                              (attrib == 0 & unattrib == 0) ~ 'no',
                              TRUE ~ NA_character_)
         )
```

```{r first_samples}
multi_samples <-
  metadat %>% 
  group_by(subject_id) %>% 
  tally() %>% 
  filter(n > 1)
